Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Escape spaces after "\meek".
Just like 24146bba0601b5e6a7393d22985ea4a50deeb0fa.

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek combines fronting with a proxy server that encodes a TCP stream
as a sequence of HTTP requests and responses.
The \meek server's external interface is that of an ordinary web server.
Domain fronting enables a client to reach the server.
The server receives requests, decodes them, and feeds their payloads into a Tor relay,
and returns downstream data in the HTTP response.
A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
We describe the results of an initial deployment.
\meek, or something based on it,
has been adopted by other circumvention systems including Lantern and Psiphon.

@@

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as pluggable transport~\cite{pt} for Tor.
\meek combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into the Tor network.
Downstream data received from Tor
are returned to the client as HTTP responses.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes how it works in detail.

@@

\meek has been built into an alpha version of Tor Browser,
and has a small number of users.
Our deployment so far uses Google App Engine and Amazon CloudFront.
% with the hidden actual domain \urll{meek-reflect.appspot.com}
% hidden by the front \urll{www.google.com}.
Section~\ref{sec:deployment} discusses other fronting-capable services
and deployment scenarios.
In addition to the Tor pluggable transport,
systems based on \meek are now used by other circumvention systems
including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

% \meek is designed to have features attractive in a circumvention transport.
% It is easy to use, not requiring the configuration of any bridge addresses.
% In Tor Browser, users need only select ``meek''
% from a pulldown menu in order to use it.
% It resists blocking by address and by content,
% Section~\ref{sec:discussion}

Domain fronting and HTTPS take care of two big circumvention challenges,
those of hiding the destination and of obscuring the contents of a message.
There remain other, more subtle, attributes of communication
that could serve as a basis for blocking.
For example, the plaintext handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
to make \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
One of our goals is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than simple domain blacklists or deep packet inspection;
to force the practice of censorship to exist in a world
not of simple packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to detection
based on traffic characteristics like packet length distribution
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of \meek
with samples of HTTPS traffic at an Internet router.

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek uses just a few high-value front domains on hard-to-block network infrastructure.
A quirk of the browser proxy model is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

@@

GoAgent~\cite{goagent} is a direct inspiration for \meek in its use of
domain fronting with App Engine.
Traffic is fronted by the Google frontend server,
using the ``domainless'' fronting model without SNI,
and delivered to its destination by a specialized app running on App Engine.
GoAgent doesn't use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
and the contents of all communications are revealed to Google.
Users of GoAgent generally upload their own personal copy of the proxy code to App Engine,
which is free of charge to use as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek over App Engine was similarly affected.
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

The components of the system are shown in Figure~\ref{fig:architecture}.
The parts that are new in \meek
are the programs \meekclient and \meekserver,
which are the pluggable-transports~\cite{pt} interface with Tor.

@@

When \meek is used with Google App Engine, one other component is needed:
a small ``reflector'' web app that simply copies any request
it receives and forwards it to a remote instance of \meekserver.
App Engine cannot directly run a Tor bridge,
so we bounce the requests to somewhere that can.
The reflector app emulates the behavior of an origin-pull CDN,
which also simply copies and forwards requests
when the response is not already cached.

The main technical challenge of the protocol is splitting up a TCP stream
into a sequence of HTTP requests and responses.
The underlying TCP stream is broken into chunks so that
it can be sent over HTTP.
The body of each HTTP request and HTTP response carries
a small chunk of upstream or downstream communication.
There must therefore be some way of making sure that chunks
are correctly reassembled at the other end,
in order and without gaps and duplicates.
\meek takes a naive approach: requests and responses are strictly serialized.
The client doesn't send a second chunk of data
(i.e, make another HTTPS request) until it has
received the response to its first.
The reconstructed stream is simply the concatenation
of bodies in the order they arrive.
Doing it this way is simple and guarantees correctness,
but has performance drawbacks because there is a full round-trip
between every send.
Section~\ref{sec:discussion} proposes a more efficient encoding
that would enable multiple requests in parallel.

@@

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and X-Session-Id headers for classification.
}
\label{fig:protocol}
\end{figure}

@@

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
\meek uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send,
simply to give the server an opportunity to reply.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
The other technique,
implemented in Psiphon's version of \meek,
uses long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response stream it has open to the client and starts a new one.
This second technique is especially beneficial for bulk downloads,
but doesn't work on all services:
notably Google App Engine doesn't support streaming of this kind.

@@

\begin{center}
\begin{tabular}{r@{}r l}
          &    514 & Tor cell \\
          &  $+$29 & Tor TLS record \\
$\approx$ & $+$400 & \meek HTTP header \\
$\approx$ &  $+$50 & \meek TLS record \\
\hline
$\approx$ &   1000 & total
\end{tabular}
\end{center}

@@

The TLS handshake is largely plaintext~\cite[Section~7.4]{rfc5246}, and leaves
enough room for variation, for example in
the client's lists of ciphersuites and extensions,
that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}
based on the handshake.
(We are only concerned with fingerprinting the client,
because the server's TLS
comes from the intermediate web service;
i.e., it is what you would expect to see when connecting to the front domain.)
Tor itself was blocked by China in 2011
because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
Figure~\ref{fig:ciphersuites} shows examples of how TLS client
implementations may detectably differ.
\meekclient is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear on the network with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
which are browsers, are different from Go's TLS; the browsers are also unlike each other.
A censor could block an uncamouflaged \meek using Go's fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

@@

The use of a browser extension brings benefits beyond TLS camouflage.
It means \meek's HTTP tunnel inherits other characteristics of the browser:
for instance
how often it resolves DNS names,
its connection reuse,
and its HTTP keepalive behavior.
The Firefox extension has special advantages
when \meek is used with Tor Browser
because Tor Browser
is a modified version of Firefox:
we can use the same browser executable for both the browser the user interacts with (Tor Browser)
and the one providing TLS camouflage (headless Firefox),
saving space in distribution packages
and sparing the user from having to separately configure a browser to run the extension.
In Tor Browser,
the headless Firefox is started and stopped transparently
when \meek is activated and deactivated.

@@

This section contains a brief survey of fronting-capable
web services we have found, each with its pros and cons.
The list is not exhaustive and is meant to illustrate the broad
support for fronting that exists.
Of the services listed, we have so far deployed \meek
only on Google App Engine and Amazon CloudFront.
For the others, we have only checked that fronting works.
Recall that even web services that support fronting
will front only for their own customers,
so new each deployment typically means becoming a customer and an investment of time and money.

@@

CloudFlare~\cite{cloudflare},
not to be confused with CloudFront,
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom user-selected domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be popular
(causing high collateral damage if blocked),
or else the censor may simply block the domain entirely.
It is doubly bad when a domain is blocked, because not only is circumvention foiled,
but some unsuspecting third party has just had their web site blocked.
A solution may be to round-robin through
a pool of popular domain names;
or to use ``domainless'' fronting that doesn't send SNI.
% Though CloudFlare supports domain fronting,
% its terms of service~\cite{cloudflare-terms}
% seem to prohibit the kind of tunneled proxying that \meek does:
% \begin{quote}
% \textsc{Section 10: Limitation on non-HTML caching}\\
% You acknowledge that CloudFlare's Service is offered as a platform to cache and
% serve web pages and websites and is not offered for other purposes
% \ldots\ you understand and agree to use the Service solely
% for the purpose of hosting and serving web pages\ldots
% \end{quote}

@@

One of our goals in developing \meek is to force
the censor to use relatively more expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe \meek is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
We hope that the censor will have to resort to measuring
more subtle features of the communication.
In this section we provide a preliminary analysis
of \meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

@@

% Advantage is that we are probably proxying web traffic.
As \meek is based on HTTPS,
we compare traffic traces of \meek against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
of automatically browsing the home pages
of the top 500 Alexa web sites using \meek in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek trace is 687~megabytes in all
and covers about 4.5 hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized 10-minute trace
from 
%Lawrence Berkeley National Laboratory (\lbl)
a research lab (anonymized as \lbl for blind submission),
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The \lbl trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we received the trace.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
%         811         783         151        1263
% 0.012312668 0.007811963 0.007031241 0.006569205
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{\lbl Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 2.9\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the \lbl traffic trace,
and \meek running on App Engine, fronted through www.google.com.
% The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

@@

Protocols vary in their packet lengths;
a censor may block a circumvention protocol if its length distribution
is distinct enough.
Figure~\ref{fig:datalen}
compares the packet length distributions of both sample traffic traces.
In both cases, about 38\% of packets have an empty payload, mostly ACKs.
There is a small peak in both traces at the usual TCP Maximum Segment Size
of 1460 bytes.
The concentration of values near 1418 bytes
may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
% https://github.com/joyent/node/issues/6889
% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
Conspicuous in the \meek trace are a small number of
frequent packet sizes,
and the lack of a cluster of small payload lengths of around 50 bytes.
Both of these characteristics are probably artifacts
of Tor's fixed cell size and the nearly fixed-size HTTP headers
added by \meekclient and \meekserver.
% In this trace, packets of 1024 bytes are probably single
% Tor cells and those of 396 are probably empty polling requests.

% David: I don't think the following paragraph is true.
% Almost all the length>1400 packets are Google→client, not client→Google,
% as you can see if you split the histogram up by direction.
%
% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for \meek in order
% to hide TLS handshake characteristics.
% Browsers also apply techniques like HTTP pipelining to improve performance. Since \meek is always communicating with
% the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
% can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
% records \meek's traffic.
% In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
% Google, click a result, and then close the tab that displays search results. The browser may close the 
% connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
% opens a new connection. In this case, small requests do not have such opportunity for batching.

% These browser techniques improve performance, but also pose unexpected consequences. 
% Although \meek alters the packet size distribution of underlying Tor traffic, 
% the censor may be aware of the distribution of \meek itself. 
% Additionally, the persistent connection itself can be an issue.
% We thus investigated other related characteristics.

@@

The \meek trace shows a propensity for longer connections.
Over 4.5 hours, there were only 10 connections,
three of them lasting for an hour.
The long connections are caused by the client browser extension's
use of long-lived HTTP keepalive connections,
combined with \meekclient's polling requests,
which keep the connection from becoming idle.
The traffic trace represents the browsing of hundreds of web sites
and thousands of HTTPS transactions, but they all
occurred over just a few TCP/TLS connections.
60\% of \meek connections lasts five minutes or longer,
while only 13\% of those of ordinary traffic do.
\meek has essentially no connections lasting less than 24 seconds,
but such short connections account for over 42\% of the \lbl HTTPS connections.
30\% (3 out of 10) of \meek's connections lasted almost exactly one hour,
evidently reflecting a built-in time limit in either the client browser extension
or in App Engine.

>>>>

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek\ combines fronting with a proxy server that encodes a TCP stream
as a sequence of HTTP requests and responses.
The \meek\ server's external interface is that of an ordinary web server.
Domain fronting enables a client to reach the server.
The server receives requests, decodes them, and feeds their payloads into a Tor relay,
and returns downstream data in the HTTP response.
A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
We describe the results of an initial deployment.
\meek, or something based on it,
has been adopted by other circumvention systems including Lantern and Psiphon.

@@

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as pluggable transport~\cite{pt} for Tor.
\meek\ combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into the Tor network.
Downstream data received from Tor
are returned to the client as HTTP responses.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes how it works in detail.

@@

\meek\ has been built into an alpha version of Tor Browser,
and has a small number of users.
Our deployment so far uses Google App Engine and Amazon CloudFront.
% with the hidden actual domain \urll{meek-reflect.appspot.com}
% hidden by the front \urll{www.google.com}.
Section~\ref{sec:deployment} discusses other fronting-capable services
and deployment scenarios.
In addition to the Tor pluggable transport,
systems based on \meek\ are now used by other circumvention systems
including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

% \meek\ is designed to have features attractive in a circumvention transport.
% It is easy to use, not requiring the configuration of any bridge addresses.
% In Tor Browser, users need only select ``meek''
% from a pulldown menu in order to use it.
% It resists blocking by address and by content,
% Section~\ref{sec:discussion}

Domain fronting and HTTPS take care of two big circumvention challenges,
those of hiding the destination and of obscuring the contents of a message.
There remain other, more subtle, attributes of communication
that could serve as a basis for blocking.
For example, the plaintext handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
to make \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
One of our goals is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than simple domain blacklists or deep packet inspection;
to force the practice of censorship to exist in a world
not of simple packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to detection
based on traffic characteristics like packet length distribution
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of \meek\
with samples of HTTPS traffic at an Internet router.

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek\ uses just a few high-value front domains on hard-to-block network infrastructure.
A quirk of the browser proxy model is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

@@

GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of
domain fronting with App Engine.
Traffic is fronted by the Google frontend server,
using the ``domainless'' fronting model without SNI,
and delivered to its destination by a specialized app running on App Engine.
GoAgent doesn't use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
and the contents of all communications are revealed to Google.
Users of GoAgent generally upload their own personal copy of the proxy code to App Engine,
which is free of charge to use as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek\ over App Engine was similarly affected.
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

The components of the system are shown in Figure~\ref{fig:architecture}.
The parts that are new in \meek\
are the programs \meekclient and \meekserver,
which are the pluggable-transports~\cite{pt} interface with Tor.

@@

When \meek\ is used with Google App Engine, one other component is needed:
a small ``reflector'' web app that simply copies any request
it receives and forwards it to a remote instance of \meekserver.
App Engine cannot directly run a Tor bridge,
so we bounce the requests to somewhere that can.
The reflector app emulates the behavior of an origin-pull CDN,
which also simply copies and forwards requests
when the response is not already cached.

The main technical challenge of the protocol is splitting up a TCP stream
into a sequence of HTTP requests and responses.
The underlying TCP stream is broken into chunks so that
it can be sent over HTTP.
The body of each HTTP request and HTTP response carries
a small chunk of upstream or downstream communication.
There must therefore be some way of making sure that chunks
are correctly reassembled at the other end,
in order and without gaps and duplicates.
\meek\ takes a naive approach: requests and responses are strictly serialized.
The client doesn't send a second chunk of data
(i.e, make another HTTPS request) until it has
received the response to its first.
The reconstructed stream is simply the concatenation
of bodies in the order they arrive.
Doing it this way is simple and guarantees correctness,
but has performance drawbacks because there is a full round-trip
between every send.
Section~\ref{sec:discussion} proposes a more efficient encoding
that would enable multiple requests in parallel.

@@

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84\x25...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek\ HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and X-Session-Id headers for classification.
}
\label{fig:protocol}
\end{figure}

@@

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
\meek\ uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send,
simply to give the server an opportunity to reply.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
The other technique,
implemented in Psiphon's version of \meek,
uses long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response stream it has open to the client and starts a new one.
This second technique is especially beneficial for bulk downloads,
but doesn't work on all services:
notably Google App Engine doesn't support streaming of this kind.

@@

\begin{center}
\begin{tabular}{r@{}r l}
          &    514 & Tor cell \\
          &  $+$29 & Tor TLS record \\
$\approx$ & $+$400 & \meek\ HTTP header \\
$\approx$ &  $+$50 & \meek\ TLS record \\
\hline
$\approx$ &   1000 & total
\end{tabular}
\end{center}

@@

The TLS handshake is largely plaintext~\cite[Section~7.4]{rfc5246}, and leaves
enough room for variation, for example in
the client's lists of ciphersuites and extensions,
that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}
based on the handshake.
(We are only concerned with fingerprinting the client,
because the server's TLS
comes from the intermediate web service;
i.e., it is what you would expect to see when connecting to the front domain.)
Tor itself was blocked by China in 2011
because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
Figure~\ref{fig:ciphersuites} shows examples of how TLS client
implementations may detectably differ.
\meekclient is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear on the network with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
which are browsers, are different from Go's TLS; the browsers are also unlike each other.
A censor could block an uncamouflaged \meek\ using Go's fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

@@

The use of a browser extension brings benefits beyond TLS camouflage.
It means \meek's HTTP tunnel inherits other characteristics of the browser:
for instance
how often it resolves DNS names,
its connection reuse,
and its HTTP keepalive behavior.
The Firefox extension has special advantages
when \meek\ is used with Tor Browser
because Tor Browser
is a modified version of Firefox:
we can use the same browser executable for both the browser the user interacts with (Tor Browser)
and the one providing TLS camouflage (headless Firefox),
saving space in distribution packages
and sparing the user from having to separately configure a browser to run the extension.
In Tor Browser,
the headless Firefox is started and stopped transparently
when \meek\ is activated and deactivated.

@@

This section contains a brief survey of fronting-capable
web services we have found, each with its pros and cons.
The list is not exhaustive and is meant to illustrate the broad
support for fronting that exists.
Of the services listed, we have so far deployed \meek\
only on Google App Engine and Amazon CloudFront.
For the others, we have only checked that fronting works.
Recall that even web services that support fronting
will front only for their own customers,
so new each deployment typically means becoming a customer and an investment of time and money.

@@

CloudFlare~\cite{cloudflare},
not to be confused with CloudFront,
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom user-selected domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be popular
(causing high collateral damage if blocked),
or else the censor may simply block the domain entirely.
It is doubly bad when a domain is blocked, because not only is circumvention foiled,
but some unsuspecting third party has just had their web site blocked.
A solution may be to round-robin through
a pool of popular domain names;
or to use ``domainless'' fronting that doesn't send SNI.
% Though CloudFlare supports domain fronting,
% its terms of service~\cite{cloudflare-terms}
% seem to prohibit the kind of tunneled proxying that \meek\ does:
% \begin{quote}
% \textsc{Section 10: Limitation on non-HTML caching}\\
% You acknowledge that CloudFlare's Service is offered as a platform to cache and
% serve web pages and websites and is not offered for other purposes
% \ldots\ you understand and agree to use the Service solely
% for the purpose of hosting and serving web pages\ldots
% \end{quote}

@@

One of our goals in developing \meek\ is to force
the censor to use relatively more expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe \meek\ is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
We hope that the censor will have to resort to measuring
more subtle features of the communication.
In this section we provide a preliminary analysis
of \meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

@@

% Advantage is that we are probably proxying web traffic.
As \meek\ is based on HTTPS,
we compare traffic traces of \meek\ against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
of automatically browsing the home pages
of the top 500 Alexa web sites using \meek\ in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek\ trace is 687~megabytes in all
and covers about 4.5 hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized 10-minute trace
from 
%Lawrence Berkeley National Laboratory (\lbl)
a research lab (anonymized as \lbl for blind submission),
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The \lbl trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we received the trace.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
%         811         783         151        1263
% 0.012312668 0.007811963 0.007031241 0.006569205
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{\lbl Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 2.9\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the \lbl traffic trace,
and \meek\ running on App Engine, fronted through www.google.com.
% The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

@@

Protocols vary in their packet lengths;
a censor may block a circumvention protocol if its length distribution
is distinct enough.
Figure~\ref{fig:datalen}
compares the packet length distributions of both sample traffic traces.
In both cases, about 38\% of packets have an empty payload, mostly ACKs.
There is a small peak in both traces at the usual TCP Maximum Segment Size
of 1460 bytes.
The concentration of values near 1418 bytes
may be caused by Google servers' sizing of TLS records so they fit within TCP segments.
% https://github.com/joyent/node/issues/6889
% http://mailman.nginx.org/pipermail/nginx-devel/2013-December/004703.html
Conspicuous in the \meek\ trace are a small number of
frequent packet sizes,
and the lack of a cluster of small payload lengths of around 50 bytes.
Both of these characteristics are probably artifacts
of Tor's fixed cell size and the nearly fixed-size HTTP headers
added by \meekclient and \meekserver.
% In this trace, packets of 1024 bytes are probably single
% Tor cells and those of 396 are probably empty polling requests.

% David: I don't think the following paragraph is true.
% Almost all the length>1400 packets are Google→client, not client→Google,
% as you can see if you split the histogram up by direction.
%
% To explain the phenomenon, recall that we use browsers to handle HTTPS connections for \meek\ in order
% to hide TLS handshake characteristics.
% Browsers also apply techniques like HTTP pipelining to improve performance. Since \meek\ is always communicating with
% the same Google frontend server, the browser will keep the persistent TLS connection. In addition, small requests 
% can be batched into a large chunk before being sent. This explains why large packets are mostly seen from the trace that
% records \meek's traffic.
% In contrast, normal users may not have persistent connections to Google. For example, a user may search a keyword on
% Google, click a result, and then close the tab that displays search results. The browser may close the 
% connection immediately after the user leaves the Google web page. Next time the user browses Google search, the browser 
% opens a new connection. In this case, small requests do not have such opportunity for batching.

% These browser techniques improve performance, but also pose unexpected consequences. 
% Although \meek\ alters the packet size distribution of underlying Tor traffic, 
% the censor may be aware of the distribution of \meek\ itself. 
% Additionally, the persistent connection itself can be an issue.
% We thus investigated other related characteristics.

@@

The \meek\ trace shows a propensity for longer connections.
Over 4.5 hours, there were only 10 connections,
three of them lasting for an hour.
The long connections are caused by the client browser extension's
use of long-lived HTTP keepalive connections,
combined with \meekclient's polling requests,
which keep the connection from becoming idle.
The traffic trace represents the browsing of hundreds of web sites
and thousands of HTTPS transactions, but they all
occurred over just a few TCP/TLS connections.
60\% of \meek\ connections lasts five minutes or longer,
while only 13\% of those of ordinary traffic do.
\meek\ has essentially no connections lasting less than 24 seconds,
but such short connections account for over 42\% of the \lbl HTTPS connections.
30\% (3 out of 10) of \meek's connections lasted almost exactly one hour,
evidently reflecting a built-in time limit in either the client browser extension
or in App Engine.
